---
title: "Coordinate systems"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Coordinate systems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(leaflet)
library(leaflet.indoor)
```

Indoor data commonly use either geographic coordinates tied to the Earth or
local Cartesian coordinates tied only to a floor plan. These are separate
workflows and are never converted into each other automatically.

## Geographic coordinates

For an ordinary Leaflet map, `sf` data must have a declared CRS. Projected and
geographic data are transformed to EPSG:4326 before serialization.

```{r geographic, out.width='100%'}
leaflet(indoor_demo_geo) |>
  addIndoor(label = ~name, style = list(fillColor = ~fill)) |>
  addIndoorControl()
```

GeoJSON follows the same longitude and latitude interpretation. Geographic
longitude must be in `[-180, 180]` and latitude in `[-90, 90]`.

## Local Cartesian coordinates

Local plans use `L.CRS.Simple`. The `sf` CRS must be undefined and
`crs = "simple"` makes the coordinate interpretation explicit. The x coordinate
is passed as Leaflet longitude and y as Leaflet latitude, which is how
`L.CRS.Simple` represents a Cartesian plane.

```{r simple, out.width='100%'}
leaflet(
  indoor_demo,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.Simple"),
    minZoom = -2
  )
) |>
  addIndoor(
    label = ~name,
    style = list(fillColor = ~fill),
    crs = "simple"
  ) |>
  addIndoorControl(position = "bottomright")
```

The package does not assign a CRS to a local plan, georeference an image, or
guess a transformation. Users who need a geographic map must establish that
relationship from authoritative control points outside `leaflet.indoor`.

## Proxies

A `leafletProxy()` object does not contain the rendered map's CRS options.
Geographic `sf` data with a declared CRS remain unambiguous. Local `sf` data
without a CRS require `crs = "simple"` when added through a proxy.
