---
title: "Indoor data formats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Indoor data formats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(leaflet)
library(leaflet.indoor)
library(sf)
```

## Simple features

An `sf` object is the preferred input. The geometry may contain points,
multipoints, lines, multilines, polygons, multipolygons, and compatible geometry
collections. Each non-empty feature needs at least one floor.

```{r sf-summary}
table(sf::st_geometry_type(indoor_demo, by_geometry = TRUE))
```

The floor column may be numeric, character, or factor. Use a list-column for a
feature shared across floors:

```r
rooms$level <- list(c("0", "1"), "1", c("1", "2"))
```

A bare `sfc` has no attributes, so pass one floor value per geometry:

```{r sfc-example, eval=TRUE}
geometry <- st_geometry(indoor_demo[1:2, ])
leaflet(options = leafletOptions(crs = leafletCRS("L.CRS.Simple"))) |>
  addIndoor(data = geometry, level = c("0", "1"), crs = "simple")
```

## GeoJSON

`addIndoor()` accepts a local `.geojson` file, a JSON string, an R list
representing a `Feature` or `FeatureCollection`, or a list of features. Remote
URLs are intentionally not downloaded.

GeoJSON properties are available to `label`, `popup`, `layerId`, and `style`
formulas. Under an ordinary map, GeoJSON coordinates are interpreted as
longitude and latitude. Use `crs = "simple"` for a local coordinate structure.

```{r geojson-example, eval=TRUE}
geojson_file <- tempfile(fileext = ".geojson")
geojson_demo <- indoor_demo_geo[c(1:3, 6:10), ]
geojson_demo$level <- vapply(geojson_demo$level, `[[`, character(1), 1)
sf::st_write(geojson_demo, geojson_file, quiet = TRUE)

leaflet() |>
  addIndoor(
    data = geojson_file,
    label = ~name,
    popup = ~description,
    layerId = ~feature_id
  ) |>
  addIndoorControl()
```

## SpatVector

When the suggested `terra` package is installed, `SpatVector` input is converted
with `sf::st_as_sf()`. Attributes and the declared CRS are then handled exactly
like ordinary `sf` input.

```{r terra-example, eval=FALSE}
rooms_terra <- terra::vect(indoor_demo_geo)
leaflet() |>
  addIndoor(rooms_terra, label = ~name) |>
  addIndoorControl()
```

## Empty and invalid data

A zero-row feature collection is valid and creates an empty indoor data set.
Its control displays `No levels`. Individual empty geometries, unsupported curve
types, non-finite coordinates, duplicate `layerId` values, and malformed
GeoJSON are rejected with feature-specific errors.
