---
title: "Get started with leaflet.indoor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with leaflet.indoor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(leaflet)
library(leaflet.indoor)
```

`leaflet.indoor` adds indoor vector layers to a `leaflet` map and keeps one
floor visible per indoor data set. It works with saved HTML widgets, R Markdown,
Quarto, and Shiny without a tile service.

## Data structure

The primary input is an `sf` object. A column named `level` is used by default.
Numeric, character, and factor floors are supported. A list-column assigns one
feature to more than one floor:

```{r levels}
indoor_demo[c("name", "level")]
```

The included data are synthetic. Rooms use polygons, the corridor and emergency
route use line geometries, the elevator uses a point, and the sensor feature is
a multipoint. The stairwell and elevator belong to floors 0, 1, and 2.

Missing or empty floors are errors by default. Use
`missing_level = "drop"` only when dropping incomplete features is intentional.

## A local Cartesian map

Local plans must use `L.CRS.Simple`, have no declared `sf` CRS, and explicitly
set `crs = "simple"`. Coordinates are passed through unchanged.

```{r local-map, out.width='100%'}
leaflet(
  indoor_demo,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.Simple"),
    minZoom = -2
  )
) |>
  addIndoor(
    level = "level",
    initial_level = "0",
    layerId = ~feature_id,
    label = ~name,
    popup = ~description,
    style = list(fillColor = ~fill),
    crs = "simple"
  ) |>
  addIndoorControl(position = "bottomright")
```

## Floor order

Pure numeric levels are ordered numerically. Character levels use a stable
natural order, including basements such as `B2` and `B1`. Factor levels retain
their observed factor order. For domain-specific labels, provide every observed
floor exactly once:

```r
addIndoor(
  level_order = c("Basement", "Ground", "Mezzanine", "Upper"),
  initial_level = "Ground"
)
```

The canonical order runs from lowest to highest. The vertical control displays
the reverse order by default so higher floors appear above lower floors. Set
`indoorControlOptions(descending = FALSE)` to display canonical order.

## Styles, labels, and popups

`indoorOptions()` defines separate defaults for points, lines, and polygons.
The `style` list can contain constants, vectors, or formulas. Its values override
the geometry defaults feature by feature.

Plain labels and popups are escaped. Mark up trusted content explicitly:

```r
addIndoor(
  label = ~name,
  popup = htmltools::HTML("<strong>Trusted content</strong>"),
  style = list(fillColor = ~fill, weight = 2)
)
```

For paired room images and captions, see the
`vignette("photo-carousels", package = "leaflet.indoor")` article.

## Multiple indoor data sets

Data sets are independent when they use different `dataset_id` values. Controls
are independent when they use different `control_id` values. Identifiers are
scoped to one map, so separate widgets never share an active floor.

```r
map |>
  addIndoor(data = rooms, dataset_id = "rooms") |>
  addIndoorControl(dataset_id = "rooms", control_id = "rooms-control") |>
  addIndoor(data = services, dataset_id = "services") |>
  addIndoorControl(dataset_id = "services", control_id = "services-control")
```

## Geographic data

`sf` objects with a declared geographic or projected CRS are transformed to
EPSG:4326 for an ordinary Leaflet map. This example intentionally omits online
tiles so it builds without network access.

```{r geographic-map, out.width='100%'}
leaflet(indoor_demo_geo) |>
  addIndoor(
    layerId = ~feature_id,
    label = ~name,
    popup = ~description,
    style = list(fillColor = ~fill)
  ) |>
  addIndoorControl()
```

## Shiny and proxies

Use `setIndoorLevel()` with a proxy after a map has rendered:

```r
leafletProxy("map") |>
  setIndoorLevel("2")
```

User changes arrive in `input$map_indoor_level` as a list containing `level`,
`dataset_id`, and `control_id`. See `vignette("shiny", package =
"leaflet.indoor")` for a complete application.

## Troubleshooting

* A missing `level` column is an error and names the missing column.
* A local plan on a geographic map is rejected instead of being silently
  interpreted as longitude and latitude.
* A spatial CRS on an `L.CRS.Simple` map is rejected because no defensible
  spatial transformation exists.
* An unknown floor passed to a regular map is an R error. On a Shiny proxy it is
  rejected in the browser and leaves the current floor unchanged.

## Known limitations and roadmap

Version 0.1.0 supports two-dimensional GeoJSON-compatible vector geometry. It
does not provide rasters, three-dimensional floors, indoor routing, feature
editing, or automatic alignment of unrelated floor plans. Future work will be
driven by reproducible use cases and compatibility with the Leaflet JavaScript
version embedded by the R `leaflet` package.
