---
title: "A real-world indoor map with room photos"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A real-world indoor map with room photos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(leaflet)
library(leaflet.indoor)
library(sf)
```

This example uses a real place, real indoor geometry, a real Leaflet base map,
and real photographs. It combines 135 named indoor spaces at the Louvre Museum
in Paris from a dated OpenStreetMap snapshot with two Wikimedia Commons
photographs of the Salle des Caryatides.

The example is intended to demonstrate the software, not to replace the
Louvre's official visitor, accessibility, evacuation, or safety information.
OpenStreetMap is maintained by contributors and indoor details can change.

## Inspect the real room data

The bundled GeoJSON uses EPSG:4326 coordinates. Its 135 polygons cover three
OpenStreetMap levels and retain the source way identifiers needed for
traceability. The source snapshot is bundled in `data-raw/`, so rebuilding the
example does not silently replace the plan with newer community edits.

```{r real-data}
room_file <- system.file(
  "examples", "real", "louvre-rooms.geojson",
  package = "leaflet.indoor"
)
louvre_rooms <- st_read(room_file, quiet = TRUE)

table(louvre_rooms$level)
head(st_drop_geometry(louvre_rooms)[c("feature_id", "level", "name")])
```

The mapped spaces include the Hall Napoléon, the Salle de la Vénus de Milo,
the Salle des Caryatides, the Galerie d'Apollon, and the Grande Galerie. The
room names and geometries are those recorded in the cited OpenStreetMap ways,
not manually invented coordinates.

## Associate photographs with a room

Use one catalogue row per image. Repeating the room identifier produces a
carousel in row order. Here, both rows target OpenStreetMap way 394887893, the
Salle des Caryatides.

```{r real-photos}
photo_directory <- system.file(
  "examples", "real", "photos",
  package = "leaflet.indoor"
)

louvre_photos <- indoorPhotoCatalog(
  layerId = rep("osm-way-394887893", 2),
  src = file.path(photo_directory, c(
    "louvre-caryatides-main.jpg",
    "louvre-caryatides-reopening.jpg"
  )),
  caption = c(
    paste(
      "Salle des Caryatides, photographed in 2024.",
      "Photo: Wilfredor, CC0 1.0, via Wikimedia Commons."
    ),
    paste(
      "Salle des Caryatides shortly after the Louvre reopened in 2021.",
      "Photo: Tangopaso, public domain, via Wikimedia Commons."
    )
  ),
  alt = c(
    "Wide interior view of the Salle des Caryatides at the Louvre",
    "Interior of the Salle des Caryatides with few visitors"
  )
)

data.frame(
  layerId = louvre_photos$layerId,
  caption = louvre_photos$caption
)
```

Existing local images are embedded as image data URIs. The interactive map is
therefore portable even though the source files are local package assets.

## Explore the map

Select level `0`, then click the red Salle des Caryatides polygon. The popup
keeps the ordinary room description and adds the two-photo carousel. Use
Previous and Next to change photos, and Enlarge to open the current image with
its matching caption. Rooms without catalogue rows retain their ordinary
popup.

```{r real-map, out.width='100%'}
louvre_rooms$fill <- ifelse(
  louvre_rooms$name == "Salle des Caryatides",
  "#c43c2e",
  c(`-2` = "#6b7280", `0` = "#2f7d65", `1` = "#3568a8")[louvre_rooms$level]
)

leaflet(louvre_rooms) |>
  addTiles() |>
  addIndoor(
    level = "level",
    level_order = c("-2", "0", "1"),
    initial_level = "0",
    layerId = ~feature_id,
    photos = louvre_photos,
    label = ~name,
    popup = ~paste0(name, ". Level ", level, ". ", description),
    style = list(
      color = "#17324d",
      weight = 2,
      fillColor = ~fill,
      fillOpacity = 0.72
    ),
    popupOptions = popupOptions(keepInView = TRUE)
  ) |>
  addIndoorControl(
    position = "bottomright",
    options = indoorControlOptions(title = "Louvre level")
  )
```

This rendered map exercises the geographic path of `addIndoor()`: real
longitude and latitude coordinates are displayed over live OpenStreetMap
tiles, exactly one floor is active, and photographs are joined through the
same stable identifiers used by the vector features.

## Data and image provenance

The source extract was downloaded on 2026-09-08 from the official OpenStreetMap
API. The example selects all 135 named indoor rooms or areas on levels `-2`,
`0`, and `1` within that extract. OpenStreetMap data is copyright OpenStreetMap
contributors and licensed under the
[ODbL 1.0](https://opendatacommons.org/licenses/odbl/1-0/). See the
[OpenStreetMap copyright page](https://www.openstreetmap.org/copyright).

The first photograph is by Wilfredor and is available under
[CC0 1.0](https://creativecommons.org/publicdomain/zero/1.0/) on
[Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Salle_des_Caryatides,_Louvre,_Paris.jpg).
The second photograph is by Tangopaso, who dedicated it to the public domain,
and is also available on
[Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Salle_des_Caryatides_d%C3%A9serte_%C3%A0_la_r%C3%A9ouverture_du_Louvre.jpg).
The package includes full machine-readable source URLs and a detailed
attribution file with these example assets.

## Adapt the pattern

For another building, provide an `sf` object with stable room identifiers and a
level column, then build the same one-row-per-photo association. The optional
`alt` column should describe the image for people who cannot see it. Captions
and alternative text are treated as plain text.

All carousel labels can be translated:

```r
indoorPhotoOptions(
  previous_label = "Précédent",
  next_label = "Suivant",
  enlarge_label = "Agrandir",
  close_label = "Fermer",
  carousel_label = "Photos de la pièce",
  dialog_label = "Photo agrandie de la pièce",
  counter_label = "Photo {current} sur {total}",
  unavailable_label = "Image indisponible"
)
```

The fully offline synthetic example remains available through
`system.file("examples", "photo-carousel.R", package = "leaflet.indoor")` for
tests and environments where live map tiles are unavailable.
