---
title: "Room comments and visitor accounts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Room comments and visitor accounts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(leaflet)
library(leaflet.indoor)
```

Use a separate clickable icon to indicate that a room has comments or visitor
accounts. A room's ordinary popup and photo carousel remain available by
clicking the room itself. Only the active floor's comment icons are displayed.

## Associate comments with rooms

Use one row per comment. Repeating a `layerId` displays several comments in
catalogue order. Only rooms with catalogue entries receive an icon. The
following comments are explicitly fictional demonstration text.

```{r synthetic-comments}
room_comments <- indoorCommentCatalog(
  layerId = c("feature-01", "feature-01", "feature-06"),
  text = c(
    "A quiet place for our group discussion.",
    "The entrance was easy to find.",
    "I enjoyed the reading space upstairs."
  ),
  author = c("Example visitor A", "Example visitor B", "Example visitor C"),
  title = "Fictional demonstration comment"
)

leaflet(indoor_demo, height = 480, options = leafletOptions(
  crs = leafletCRS("L.CRS.Simple")
)) |>
  addIndoor(
    layerId = ~feature_id,
    label = ~name,
    popup = ~description,
    comments = room_comments,
    commentOptions = indoorCommentOptions(icon = "comment"),
    crs = "simple"
  ) |>
  addIndoorControl(position = "bottomright")
```

Click the purple speech bubble in the Meeting room to read two comments.
Choose floor `1` to see the Reading room's icon. Icons also work with Enter
and Space; Escape closes the comment popup and returns focus to its icon.
Long comment lists scroll within the popup.

The icon is placed on the feature surface, including concave rooms and rooms
with holes. Placement uses a planar calculation in the map's normalized
coordinates, suitable for building-scale maps.

## Choose an icon and translate the labels

The `icon` argument accepts `"comment"`, `"quote"`, and `"info"`, or a short
plain-text symbol. Built-in icons use bundled SVG paths and need no external
font or icon service. Colors use hexadecimal notation.

The badge and its icon resize together as the map zoom changes. By default,
the visual diameter fits 75% of the room's shorter projected bounding-box
dimension, bounded by `min_size = 12` and `size = 36` pixels. The minimum
preserves visibility when a room becomes very small. Point features retain
the configured size. The clickable target remains at least 44 pixels.
Use `fit_to_room = FALSE` for a fixed visual diameter, or choose different
`size` and `min_size` values.

```{r comment-options}
indoorCommentOptions(
  icon = "quote",
  background_color = "#7c3aed",
  marker_label = "Lire les témoignages",
  popup_label = "Témoignages",
  source_label = "Lire la source"
)

indoorCommentOptions(icon = "\u2605", background_color = "#0b5cab")
```

Set `show = FALSE` to retain the comments without drawing their icons, or
omit `comments` entirely. Replacing or clearing an indoor data set also
replaces or clears its comment markers. Comment fields are always plain text;
HTML-looking strings are displayed literally. Optional source links must be
absolute HTTP(S) URLs. Optional author, date, source, and title fields use
empty strings when omitted. Dates are displayed as supplied.

## Published visitor accounts at the Louvre

The bundled Louvre example includes four short excerpts or summaries from
three published first-person accounts. They are associated with three named
rooms in the dated OpenStreetMap snapshot:

| Room | Floor | Account |
| --- | --- | --- |
| Salle de la Vénus de Milo | 0 | Jitka Tupa's reflection on incomplete sculptures, explicitly labelled as a summary. |
| Salle des États | 1 | Short excerpts by `patricia_pham` (UMass Lowell) and Jitka Tupa about seeing the Mona Lisa. |
| Galerie d'Apollon | 1 | A short excerpt by Michele (Malaysian Meanders), reacting to her children sharing discoveries in the gallery. |

```{r louvre-catalogue}
louvre_comments <- read.csv(
  system.file("examples", "real", "louvre-comments.csv", package = "leaflet.indoor"),
  stringsAsFactors = FALSE,
  fileEncoding = "UTF-8"
)
louvre_comments[c("author", "date", "title")]
```

```{r louvre-map, out.width='100%'}
louvre_example <- source(
  system.file("examples", "louvre-photo-carousel.R", package = "leaflet.indoor"),
  local = new.env(parent = globalenv())
)
louvre_example$value
```

Click a purple quotation icon to read an account and follow its source link.
On floor `0`, the Vénus de Milo room also has a photograph. Click the room
away from its icon to open the photo. Select floor `1` for the Salle des États
and Galerie d'Apollon accounts. Dates shown are publication dates. These are
historical personal accounts, not a survey or a description of present-day
conditions at the museum.

Original sources, checked on 2026-10-06:

- Jitka Tupa (2015), [Visiting My Three Muses at the Louvre](https://flyingoffcourse.wordpress.com/2015/09/24/visiting-my-three-muses-at-the-louvre/).
- `patricia_pham` (2025), [A Day at the Louvre in Good Company!](https://blogs.uml.edu/paris-spring-2025/2025/03/11/a-day-at-the-louvre-in-good-company/), UMass Lowell.
- Michele (2013), [Kids and Nintendos at The Louvre](https://malaysianmeanders.blogspot.com/2013/09/nintendos-at-louvre.html).

The installed file `examples/real/COMMENT-SOURCES.md` records the exact
passages, publication dates, author attribution, and room associations.
The Louvre's official pages identify
[Salle des États](https://www.louvre.fr/decouvrir/le-palais/de-la-joconde-aux-noces-de-cana)
and the [Vénus de Milo room](https://www.louvre.fr/decouvrir/le-palais/un-ideal-de-beaute-grecque).

## Shiny

Clicking a comment icon produces `input$MAPID_indoor_comment_click`, containing
`id`, `dataset_id`, `level`, `lat`, `lng`, and `comment_count`. Ordinary room
clicks retain their separate `input$MAPID_indoor_feature_click` event.
Use `addIndoor()` on a `leafletProxy()` with the same `dataset_id` to replace
comments or change their icon options; use `setIndoorLevel()` to change the
floor, or `clearIndoor()` to remove the data set's features and icons.
