---
title: "Shiny integration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shiny integration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(leaflet)
library(leaflet.indoor)
library(shiny)
```

`leaflet.indoor` registers its dependencies on both ordinary widgets and
`leafletProxy()` calls. The application below exposes user floor changes and
updates the map from the server.

```{r shiny-app}
ui <- fluidPage(
  actionButton("floor_two", "Show floor 2"),
  verbatimTextOutput("selected_floor"),
  leafletOutput("map", height = 500)
)

server <- function(input, output, session) {
  output$map <- renderLeaflet({
    leaflet(
      indoor_demo,
      options = leafletOptions(crs = leafletCRS("L.CRS.Simple"))
    ) |>
      addIndoor(
        label = ~name,
        popup = ~description,
        layerId = ~feature_id,
        style = list(fillColor = ~fill),
        crs = "simple"
      ) |>
      addIndoorControl(position = "bottomright")
  })

  observeEvent(input$floor_two, {
    leafletProxy("map", session) |>
      setIndoorLevel("2")
  })

  output$selected_floor <- renderPrint(input$map_indoor_level)
}

app <- shinyApp(ui, server)
invisible(app)
```

Run the installed example with:

```r
shiny::runApp(system.file("examples/shiny", package = "leaflet.indoor"))
```

## Input values

User selection produces `input$MAPID_indoor_level` with:

* `level`: the selected floor as text;
* `dataset_id`: the indoor data set;
* `control_id`: the control used.

Feature clicks produce `input$MAPID_indoor_feature_click` with `id`,
`dataset_id`, `level`, `lat`, and `lng`. Programmatic floor changes do not emit
the user-selection event, which prevents reactive feedback loops.

When `comments` are supplied to `addIndoor()`, comment-icon clicks produce
`input$MAPID_indoor_comment_click` with `id`, `dataset_id`, `level`, `lat`,
`lng`, and `comment_count`. Comment icons belong to the same floor groups as
the rooms and are replaced or cleared with their indoor data set.

## Replacing and clearing data

`addIndoor()` can be called on a proxy with explicit `data`. Reusing a
`dataset_id` replaces its layer groups and refreshes linked controls.
`clearIndoor()` removes its features but retains the controls in their empty
state. `removeIndoorControl()` removes only the named control.
